\documentclass{report}

\usepackage[T1]{fontenc}       %font


\usepackage{ifthen}


\newcommand{\syscall}[5]{
\section{#1}
#2

\subsection*{Inputs}
\begin{itemize}
#3
\end{itemize}

%\ifthenelse{ \equal{#4}{} }{}{

\subsection*{Outputs}
\begin{itemize}
#4
\end{itemize}

%}

\subsection*{Other info}
#5
}



\begin{document}

\tableofcontents




\chapter{Core Calls}

\syscall{Exit - niy}{
Terminates caller process.
}{
\item EAX - status code
}{\item}{}

\syscall{ConfigEvents}{
Sets thread's event mask.
}{
\item EAX - mode
 \begin{itemize}
 \item EAX = 0 - get
 \item EAX = 1 - set
 \end{itemize}
\item EBX = mask to load, if mode 1
}{
\item EBX = current event mask, if mode 0
}{
Only one thread may wait for each event. Follows a table for the meaning of each bit.
\begin{tabular}{|c|l|}
\hline
Bit & Event\\
\hline
0	& Tidy and exit (equivalent to SIGTERM)\\
\hline
1	& KBD data available\\
\hline
?	& IPC request - niy\\
\hline
\end{tabular}
}

\syscall{WaitForEvent}{
Waits for an event to come (returns when some event requested by ConfigEvents comes).
}{\item}{
\item EAX = event id
}{
The codes are the same as the bit numbers (not the mask, but the bit numbers) for ConfigEvents. The lower the code, the more priority an event has.
}

\syscall{GetKey}{
Get's one key from the current thread's keyboard buffer, if there is one. Otherwise, returns with no key.
}{\item}{
\item EAX = Virtual Key code
\item EBX = Translated character in Unicode. Returns -1 if not a character.
}{
Obs.: If thread hasn't been configured to wait for keyboard events, no key will be read.
}


\chapter{Provisory Calls}

\syscall{GetDisplay}{
Obtains ownership of display for caller process.
}{
\item EAX - address for buffer
}{
\item EAX - error code if CF set
}{
\begin{tabular}{|c|l|}
\hline
EAX on exit & Meaning\\
\hline
1	& Conflictuous request\\
\hline
2	& Invalid address\\
\hline
\end{tabular}
}

\syscall{UpDisplay}{
Copies buffer previously set to screen. No effect if no buffer set.
}{
\item EAX - start\_line*80+start\_column
\item EBX - end\_line*80+end\_column
}{\item}{}




\end{document}




